In \cite{wardrip2009agency} \textit{Player agency} is defined as the overlapping set of what the player desires to do in a game and what is supported by the underlying computational model.\

We define \textit{Player agency} as: When a player is able to (1) control their own or their characters actions, (2) have these actions matter in the game world and (3) have sufficient information to expect the outcome of these actions. The less player agency there is in a game, the more procedural the game is. E.g. a traditional book in one end would have no agency and be completely procedural, while a table-top role-playing game controlled by a Game Master, could allow for a very high amount of player agency, depending on the flexibility of the Game Master.\

\cite{wardrip2009agency} also covers how the presence of an understandable user-interface (UI) can make players feel like they have more agency and thereby create an illusion of agency. The breakdown of this illusion of agency will then lead to the player becoming frustrated and stop playing. It does also mentioan that the the restriction of interaction can prevent this breakdown of the illusion of agency.\

We expect the players to lose interest in interacting with the battle system, once they figure out that the agency is an illusion. Still, we hope that they will be able to transcend the message of impotence in such an important situation, where you could potentially lose a dog. 
We hope this will actually make the players become involved and have a realistic experience of dog fighting, by creating some the uncomfortability and tension we discussed in section \ref{Ethics}.\

Player superstition might also play a part here. Players are generally supersticious beings, which we see when they blow the dice before rolling or click the ball when trying to catch Pok{\'e}mon in \textit{Pok{\'e}mon Go}, even if they logically know that it makes no difference on the outcome, there is still that small amount of superstition, which makes them do it. This might also make players use the mechanics, even after they logically know, that they are impotent.\

It is important to not that we do not consider this whole concept of UI allowing for impotent options to be a game mechanic, but an artistic instrument meant to create reflection and empathy in the player. \
