\subsection{Method}
To answer our hypotheses we have designed a qualitative play experience test. The procedure of the test includes first a playthrough of the game and then a semi-structured interview. The in-game choices made by the player in the playthrough is recorded as is their body language, statements or other sounds produced while playing.

The test subjects will be asked to participate in one playthrough of the game followed by a semi-structured interview to gather data on that specific play experience. Due to the mature content of the game the targeted test subjects are age 18 or above. To look for trends across genders we aim for gender equality in our sample. Furthermore while recruiting test subjects we look for subjects who has outspoken opinions about dogs, animal rights and/or human rights. The only quantitative data collected is the in-game choices of the game and these are of binary quality at best. 

In-game choices:
In the game you as player has to take several choices regarding the fate of your avatar. \commenting{Avatar or character?? it seems like it depends on the eyes that sees.. INVESTIGATE}

As mentioned in \ref{designGoals} the prototype is hard-coded so that the player will always win at least one fight and loss the fourth fight. This makes it possible for us to determine how the testers react when their dog kills another and also when their own dog dies.\

\subsection{Sessions}
Two testing sessions were conducted on the IT University of Copenhagen. The first on the 30th October 2017, the second on the 23rd November 2017. The test procedure followed the same guidelines for both of the tests however a few of the questions were rephrased and the implementation of the game underwent several changes. The changes included correction of spelling in the narrative, more graphical elements depicting the situation of the state of the game and better feedback in the dog fights in the game. These changes will have biased the test results and should be kept in mind when analysing the data.

A playthrough of the game took 10-15 min. depending on the speed of the participant - reading, taking decisions - and the random outcomes of the fights in the game. While playing the participants in-game choices was recorded. Some participants came to an end of the game after the second fight of the game others after the third.
The interview was conducted following af semi-structured questionnaire consisting of 17 predefined questions, participant demographics questions and a small observational sheet to record the actions taken by the participant in the game. Furthermore observations of the participants body language, statements and other kinds of sounds while playing the game was recorded.

\subsection{Results} \label{Results}
In total nine subjects, four male and five female, successfully participated in the test. The youngest being 24 and the oldest 31, average being 27,2 years old. Six of the participants are higher education students, two are film directors and the last participant is educated but unemployed. It is safe to conclude that the participants on average possesses intellectual judgement. In this section (\ref{Results}) the data obtained from the interviews and the play test with the participants are presented. The data has been coded and analysed for relevant trends. First observations of the players decisions in-game are presented, secondly each question are presented along with a highlight of the participants responses and a tabular representation of the participants responses to either the question or a general trend found in the data to that question. The participants are represented by number (1-9). Participants 2, 4, 6 and 7 are female, 1, 3, 5, 8 and 9 are male. 

\subsubsection{In-game Decisions}

\textbf{Sharing glue.} The first in-game decision the player has to make is whether to share the sniffing glue or not. The majority of the participants shared the glue (Table \ref{tab:glue}).

\begin{table}[h]
\centering
\begin{tabular}{l l l}
\hline
\textbf{Shared the glue?} & Yes & No \\
\hline
Male & 4 & 1 \\
Female & 2 & 2 \\
\textbf{Total} & 6 & 3 \\
\hline
\end{tabular}
\caption{\label{tab:glue}Overview of participants in-game decisions on whether to share the sniffing glue or not}
\end{table}


\textbf{Chosen protagonist name.} The second decision the participants had to make in the game was to give the protagonist a name. Six participants(1, 2, 3, 4, 5, 7) chose to give the protagonist a what we define as a serious name (Table \ref{tab:name}). The serious names are names that resemble the participants real name or is a known nickname of theirs while the non-serious names are not. We speculate that the participants chose a serious name because they want to identify with the protagonist rather than distance themselves from him. While picking a non-serious name is a way to create a humorous distance between yourself and the protagonist in the game.

\begin{table}[h]
\centering
\begin{tabular}{l l l}
\hline
\textbf{Protagonist name} & Serious & Non-serious \\
\hline
Male & 3 & 2 \\
Female & 2 & 2 \\
\textbf{Total} & 5 & 4 \\
\hline
\end{tabular}
\caption{\label{tab:name}Overview of participants choice of seriousness of protagonist name}
\end{table}


\textbf{Destiny and duration of decision.} The most important decision of the game is when the player is asked to choose their destiny. Whether they will participate in dog fighting or offer sexual favours to earn money. Six participants chose dog fighting, three chose sexual favours (Table \ref{tab:dest}). All but one of the participants made the choice relatively quickly between three to nine seconds. The one exemption, participant 2, spend a minute before choosing dog fighting.

\begin{table}[h]
\centering
\begin{tabular}{l l l}
\hline
\textbf{Chosen destiny} & Sexual favours & Dog fighting \\
\hline
Male & 1 & 4 \\
Female & 2 & 2 \\
\textbf{Total} & 3 & 6 \\
\hline
\end{tabular}
\caption{\label{tab:dest}Overview of participants in-game decisions on the destiny of the protagonist}
\end{table}


\textbf{Choice of dog.} Boxer was the favourite choice of dog among the participants. Only one participant chose the Golden Retriever. Interestingly the Husky was the favourite among the male participants (1, 3, 8) while no female participants chose it (Table \ref{tab:dog}).

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Choice of dog} & Boxer & Husky & Golden Retriever \\
\hline
Male & 2 & 3 & 0 \\
Female & 3 & 0 & 1 \\
\textbf{Total} & 5 & 3 & 1 \\
\hline
\end{tabular}
\caption{\label{tab:dog}Overview of participants choice of dog}
\end{table}


\textbf{Chosen dog name.} The chosen dog names has, like the chosen protagonist names, been divided into serious and non-serious names. Now only two participants(2, 7) chose a serious name (Table \ref{tab:dame}). 

\begin{table}[h]
\centering
\begin{tabular}{l l l}
\hline
\textbf{Dog name} & Serious & Non-serious \\
\hline
Male & 0 & 5 \\
Female & 2 & 2 \\
\textbf{Total} & 2 & 7 \\
\hline
\end{tabular}
\caption{\label{tab:dame}Overview of participants choice of seriousness of dog name}
\end{table}


\textbf{Leashing dog.} Only two participants chose to leash their dog (Table \ref{tab:leas})

\begin{table}[h]
\centering
\begin{tabular}{l l l}
\hline
\textbf{Leashed the dog?} & Yes & No \\
\hline
Male & 1 & 4 \\
Female & 1 & 3 \\
\textbf{Total} & 2 & 7 \\
\hline
\end{tabular}
\caption{\label{tab:leas}Overview of participants in-game decisions on whether to leash their dog or not}
\end{table}


\textbf{Weekly options.} Between the fights of the game the player has to take a decision on whether to try and breed their dog, catch a new dog or train their existing dog. Unfortunately this decision was not recorded for the participants(1, 2) in the first test session. However in the second test session all of the participants chose to train their dogs.


\subsubsection{Interview}
\textbf{Q1.} A trend in the respones to the question "How would you characterise the experience?" is the participants description of the emotional impact the play experience had on them, see table \ref{tab:emo}. The majority of the participants felt a negative emotional impact. Only one participant(6) does not express any emotional relation to the play experience. Her response implies that there was too much text in the game for her to be engaged. The data might indicate that either the male participants are less affected by the gloomy setting of the game.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Emotional impact from}\\
\textbf{play experience?} & Negative & Positive & Other \\
\hline
Male & 3 & 2 & 0 \\
Female & 3 & 0 & 1 \\
\textbf{Total} & 6 & 2 & 1 \\
\hline
\end{tabular}
\caption{\label{tab:emo}Emotional impact described in the responses to the question "How would you characterise the experience?"}
\end{table}

\textbf{Q2.} The responses to the question "How did you like your character?" are diverse and raises an interesting question; what is the participants perceived relation to the protagonist in the game? A trend in the data shows that the majority of the participants feels sympathy for the protagonist and/or his situation in the game (Table \ref{tab:symp}). Interestingly only two of the female participants express sympathy for the protagonist which raises the question whether the gender of the protagonist(male) has an influence on that. However studying the responses it becomes clear that the participants has different interpretations of their relationship as players towards the protagonist. Participant(4) does not really answer the question but instead respond that it is just her self making decisions, hence she did not have any emotional connection to the protagonist. Participant(3) on the other hand states that the sparse description of the protagonist enabled him to project his self onto the protagonist. A third participant(8) states that he think the kid is sweet and that he want to follow him around, implying that he does not control the protagonist but merely the circumstances in which the protagonist is placed.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Sympathy for the}\\
\textbf{protagonist?} & Yes & No & Other \\
\hline
Male & 5 & 0 & 0 \\
Female & 2 & 2 & 0 \\
\textbf{Total} & 7 & 2 & 0 \\
\hline
\end{tabular}
\caption{\label{tab:symp}Expression of sympathy towards the protagonist in the responses to the question "How did you like your character?"}
\end{table}

\commenting{Man kan godt tage en moralsk beslutning selvom begge valg er uetiske}
\textbf{Q3.}  As can be seen in table \ref{tab:choice}, the majority of the participants expressed that the moral option was to choose dog fighting over sexual favours in the game. Only one participant(4) felt sexual favours was the right option, but elaborates that her ethics might be different than the rest of the testers because of her cultural background. Participant 4 is born and raised in Hong-Kong as opposed to the rest of the testers who's ethnicity is Danish. Participant 8 chose dog fighting because he felt that the game wanted him to do so and participant 9 chose dog fighting because the man to which you can offer sexual favours was too repulsive.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Sexual favours or dog fighting,}\\
\textbf{which is the moral option?} & Sexual favours & Dog fighting & Other \\
\hline
Male & 0 & 3 & 2 \\
Female & 1 & 3 & 0 \\
\textbf{Total} & 1 & 6 & 2 \\
\hline
\end{tabular}
\caption{\label{tab:choice}Expression of moral in responses to the question "Why did you pick sexual favours or dog fighting over the other?"}
\end{table}

\textbf{Q4.} Judging from the responses to the question "Did you feel uncomfortable making the choice?" most of the participants were comfortable making their decision(Table \ref{tab:unco}). Unfortunately participant 2's response to the question is lost, but the observations recorded at her play session indicate that it was a very difficult choice for her. Apart from her body language signifying her being uncomfortable, she spend approximately one minute deciding which option to choose. In contrary the rest of the participants spend between 3-9 seconds. 

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Did you feel uncomfortable}\\
\textbf{making the choice?} & Yes & No & Other \\
\hline
Male & 1 & 4 & 0 \\
Female & 2 & 2 & 0 \\
\textbf{Total} & 3 & 6 & 0 \\
\hline
\end{tabular}
\caption{\label{tab:unco}Responses to the question "Did you feel uncomfortable making the choice?"}
\end{table}


\textbf{Q5.} The participants choice of dog described in their responses to the question "Why did you pick the dog you picked?" are coded as being either a choice based on feelings or rationale (Table \ref{tab:rati}). Six participants(2, 3, 4, 5, 6, 7, 9) made a rational decision on their choice of dog. They base their decision on which dog they felt was best capable of fighting. In contrary participant 1 and 8 based their choice of dog on feelings. Participant 1 chose the husky because he thought it was cool but speculate that the boxer might have been more capable of fighting. Participant 8 did not choose the boxer because he was too emotionally attached to it and he wouldn't want to see it suffer. His response raises the question whether the other participants seemingly rationale choices are made on the basis of choosing the dog that would suffer the least. If that is the case then the participants choices are based on feelings in the sense that they choose the dog that will have the least emotional impact on them.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Rational or emotional}\\
\textbf{choice of dog?} & Rational & Emotional & Other \\
\hline
Male & 3 & 2 & 0 \\
Female & 4 & 0 & 0 \\
\textbf{Total} & 7 & 2 & 0 \\
\hline
\end{tabular}
\caption{\label{tab:rati}Expression of rational or emotional based choice in responses to the question "Why did you pick the dog you picked?"}
\end{table}


\textbf{Q6.} As can be seen in Table \ref{tab:like}, the participants liked their dogs. Only one participant(5) express that he did not feel a relation to the dog. However he also expresses that he chose a non-serious name to avoid getting too close to the dog. Interestingly two other participants(3, 9) also express a similar rationale for choosing a non-serious name for their dog. 

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Did you like}\\
\textbf{your dog?} & Yes & No & Other \\
\hline
Male & 4 & 0 & 1 \\
Female & 4 & 0 & 0 \\
\textbf{Total} & 8 & 0 & 1 \\
\hline
\end{tabular}
\caption{\label{tab:like}Responses to the question "Did you like your dog?"}
\end{table}


\textbf{Q7.} The responses to the question "What would happen if you leashed your dog" can be divided into three categories. Leashing the dog would affect the relationship to the dog, the control over the dog or a believe that the action of leashing was a choice of right and wrong in terms of progressing in the game. The last notion has been coded as "other", see Table \ref{tab:leash}. Participant 1, 2, 3, 7 and 9 express that they believe their relationship with the dog would be improved by not leashing it. Participant 4 and 5 both express that leashing it would have made the dog easier to control, but chose to not leash it. Only two participants(6, 8) chose to leash the dog however both of them expressed that they thought it was the correct option, implying that they were afraid of the consequences in terms of progression in the game if they did not leash it.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Believed consequence of}\\
\textbf{leashing dog?} & Relationship & Control & Other \\
\hline
Male & 3 & 1 & 1 \\
Female & 2 & 1 & 1 \\
\textbf{Total} & 5 & 2 & 2 \\
\hline
\end{tabular}
\caption{\label{tab:leash}Expression of believed consequences of leashing the dog in responses to the question "What would happen if you leashed your dog?"}
\end{table}


\textbf{Q8.} Only two participants(1, 2) felt responsible for the dogs their dog killed. It is worth noting that these were the two participants who participated in the first test session which may indicate a bias. Participant 4 and 7 are vague in their responses. Participant 7 states that she felt a bit responsible but that she would rather have that the other dog died than her own dog died. (Table \ref{tab:resp})

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Did you feel responsible for}\\
\textbf{the dogs your dog killed?} & Yes & No & Other \\
\hline
Male & 1 & 4 & 0 \\
Female & 1 & 1 & 2 \\
\textbf{Total} & 2 & 5 & 2 \\
\hline
\end{tabular}
\caption{\label{tab:resp}Responses to the question "Did you feel responsible for the dogs your dog killed?"}
\end{table}


\textbf{Q9.} In general the participants express that they feel sadness when their dog died. As can be seen in table \ref{tab:sad} three participants did not have a clear cut answer to the question. Participant 4 elaborates that she had prepared herself for it the moment she caught the dog. She knew that death was inevitable, implying that she was emotionally prepared for it to happen. Her response implies that she had to emotionally detach herself from the dog to not feel sad which in turn implies that she would have felt sad if she hadn't predicted its destiny. Participant 6 felt sad when the dog died not because of any emotional attachment to the dog but because she lost the game. Lastly participant 9 express that he did not feel sad, instead he felt anger towards the dog that killed his dog. Where the anger stems from is unclear and we can only speculate that either he was in fact emotionally attached to his dog or that he, in line with participant 6, was sad that he lost the game.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Did you feel sad when}\\
\textbf{your dog died?} & Yes & No & Other \\
\hline
Male & 3 & 1 & 1 \\
Female & 2 & 0 & 2 \\
\textbf{Total} & 5 & 1 & 3 \\
\hline
\end{tabular}
\caption{\label{tab:sad}Responses to the question "Did you feel sad when your dog died?"}
\end{table}


\textbf{Q10.} The majority of the participants felt responsible for the death of their dog (Table \ref{tab:death}). Only one participant(5) states that because he tried to run from the battle it was not his responsibility. Participant 4 states that she decided that she did not wanted to feel anything. Lastly participant 6express that because she felt she was cheated she did not feel a great degree of responsibility.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Did you feel responsible for}\\
\textbf{the death of your dog?} & Yes & No & Other \\
\hline
Male & 4 & 1 & 0 \\
Female & 2 & 0 & 2 \\
\textbf{Total} & 6 & 1 & 2 \\
\hline
\end{tabular}
\caption{\label{tab:death}Responses to the question "Did you feel responsible for the death of your dog?"}
\end{table}


\textbf{Q11/Q12.} To understand the participants experience of perceived agency on the fights of the game they were asked two questions. "How does the battle system work?" and "Which options were most effective?". The participants responses to the questions has been coded as either the participant believed that hey had agency in the fights or they did not. The responses are illustrated in Table \ref{tab:agen}. Only one participant's(2) statement is unclear. She believes she can use items in the fights later in the game. However she also express that it seemed like her options had no effect. The majority of the participants believes they have agency in the fights though some of them are confused about the system. Only one participant(9) believed that he had no agency. He states that the realisation of his lack of agency came in the beginning of the second fight he was in. He states that it changed his perception of his role in the game, that he felt like he was becoming a spectator and that this notion made the message of the game stronger. His definition of the game's message is vague. He thinks the game is trying to convey that the protagonist is in a Catch-22, which in turn creates awareness about poverty and what you have to do to survive.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Perceived agency}\\
\textbf{in the fights?} & Agency & No agency & Other \\
\hline
Male & 4 & 1 & 0 \\
Female & 3 & 0 & 1 \\
\textbf{Total} & 7 & 1 & 1 \\
\hline
\end{tabular}
\caption{\label{tab:agen}Expression of perceived agency in the responses to the questions "How does the battle system work?" and "Which options were most effective?"}
\end{table}


\textbf{Q13.} To the question "Do you think it was an unethical game?", six participants(1, 2, 3, 4, 7, 9) answered no, two(5, 8) answered yes and one(6) answered that it did not matter as the game is satire (\ref{tab:ethi}). Participant 5 elaborates that he believes the Mexicans will oppose the game, but that in a sense the game is not more unethical than other games. He believes that human fights is more unethical, implying that the while unethical the game can exist under the socially accepted unethical threshold of games. Participant 8 elaborates that the humor in the game makes it very unethical, but that its existence is still justified. Participants 1, 2, 3, 4 & 7 elaborates that the game makes you are aware and puts you in the horrible situation of the game, implying that your actions are justified by the situation you are in. Participant 4 and 7's only real complaint was that they wanted a disclaimer for the blood on the dogs.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Do you think it was}\\
\textbf{an unethical game?} & Yes & No & Other \\
\hline
Male & 2 & 3 & 0 \\
Female & 0 & 3 & 1 \\
\textbf{Total} & 2 & 6 & 1 \\
\hline
\end{tabular}
\caption{\label{tab:ethi}Responses to the question "Do you think it was an unethical game?"}
\end{table}


\textbf{Q14.} When asked if the game was moralising seven participants(1, 2, 3, 5, 6, 8, 9) answered no, one(4) answered yes and the last one(7) was not sure (\ref{tab:mora}). Participants 1, 2, 3 and 5 elaborates that the game itself does not tell you what is right or wrong. Participant 4 states that the game is trying to hint something. She is not defining what the game is hinting but says the game is made to make you feel bad by dismembering and putting blood on cute dogs. Participant 7 also cannot define what the moral of the game is but that it is hard that the game forces her to downprioritise her dog.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Is the game}\\
\textbf{moralizing?} & Yes & No & Other \\
\hline
Male & 0 & 5 & 0 \\
Female & 1 & 2 & 1 \\
\textbf{Total} & 1 & 7 & 1 \\
\hline
\end{tabular}
\caption{\label{tab:mora}Responses to the question "Is the game moralising?"}
\end{table}


\textbf{Q15.} To the question "What do you think about dog fighting?" all of the participants expressed disgust of a varying degree towards it. 


\textbf{Q16.} As can be seen in Table \ref{tab:thin} six participants express that the game has made them think more about dogfighting. However four of them states that they only do so temporarily, while playing the game or only until short after having stopped playing. One participant(4) express that she does not think about dogfighting because there is nothing to do about it. Another participant(3) express that the game has made him think about the setting than the actual dogfights. He found the decision regarding sharing the glue more challenging.

\begin{table}[h]
\centering
\begin{tabular}{l l l l}
\hline
\textbf{Has this game made you think}\\
\textbf{more about dogfighting?} & Yes & No & Other \\
\hline
Male & 4 & 0 & 1 \\
Female & 2 & 1 & 1 \\
\textbf{Total} & 6 & 1 & 2 \\
\hline
\end{tabular}
\caption{\label{tab:thin}Responses to the question "Has this game made you think more about dog fighting?"}
\end{table}


\textbf{Q17.} All of the participants express, to a varying degree, that they believe dogfighters love their dogs. Participant 8 furthermore express that he believe that the dogfight spectators do not love dogs. A belief participant 2 and 4 share.


\subsection{Discussion}
The discussion of the test results will take its starting point in he research questions formulated in section \ref{ProbStat}. 


\textbf{RQ1: Can we create unethical affordances, namely dog fighting, in a game without making it an unethical game?}
The participants responses to Q13 and Q14 indicate that our game is neither perceived as being unethical nor moralising. The trend in the data shows us that the participants bought the premise of the game and felt that the situation you, or the protagonist, is placed in justifies your otherwise unethical actions \commenting{sicart ethics maybe}. Unfortunately their responses does not answer our research question in the general sense the question is asked. We know how test participants react to the game after having played it, but we do not have any data on how the common consumer will react to a game like this once it surfaces on the app stores \commenting{slave tetris}. Try to imagine going to the local mall to make a vox pop asking people whether they believe if dog fighters can love their dogs or not. We assume that you will have a significant amount of people going the "hell no" route. In contradiction all of our test participants believed that dog fighters can love their dogs. While it is all assumptions we cannot help but ask ourselves whether it is our game that has made the participants reflect on the humans in dog fighting.


\textbf{RQ2:  Will the player be able to feel empathy for the dogs, while being reliant on them fighting?}
The responses to Q17, the participants believe dogfighters can love their dogs, illustrates well that the players had or could imagine having an emotional relation to their fighting dog. 



\textbf{RQ3: How does the player feel, when they lose their dogs, while lacking the agency to prevent it?}








IS DOG FIGHTING THE BETTER ALTERNATIVE?
One of the things we were curious about is whether dog fighting is perceived as a better alternative to prostitution. It is no secret that in our - the designers - mind dog fighting is a better alternative. Our test data indicate that the majority of the participants felt the same way but we cannot ignore the data that resists this notion. A trend in the data reveals that the visual appearance of the man you are to prostitute yourself to has had an impact on the choice. We might also have to question whether the choice is affected by the player's cultural background.

One participant(2) spend a minute making the decision. She was clearly emotionally affected by the game and the choice made her feel uncomfortable. Interestingly she was part of the first test session. In the implementation of the game used for the first session the man to which you can offer sexual favours is not depicted. In the second implementation of the game he is depicted as being very repulsive.  \commenting{Insert picture of man} The fact that he is not depicted in the first test session may have made the choice less unambiguous. This thought is supported by two other participants(7, 9) statements to the question "Why did you pick dog fighting over sexual favours?". They state that the man's uglyness played a role in their decision to pick dog fighting. A fourth participant(8) states that he felt the game wanted him to choose dog fighting over sexual favours. Whether the depiction of the man has had an impact on this can only be speculated but it seems like the new implementation of the game pushes the player more towards picking dog fighting over sexual favours.

Two(1, 6) of the three participants who chose sexual favours over dog fighting stated that they chose sexual favours out of curiosity. Observations of the participants, a male and a female, indicate that they were taking the seriousness of the game lightly and were having fun with it. They seemed to have a satirical distance to the game. The male participant(1) states that he chose the sexual favours because it was more extreme. The female(2) states that her choice may have been biased because she was sitting at a test. Their data indicate that they felt that dog fighting was the moral choice but that they chose sexual favours just to see what would happen in the game. Interestingly the last participant(4) chose sexual favours because she felt that it was the moral choice. Born and raised in Hong-Kong her cultural background is different from the rest of the participants (native Danes). Her reasoning being that no one dies in the sexual favours scenario. She is aware of, and believes that her opinion and choice is different from the other test participants. However she herself states that it is because of her cultural background.

CHARACTER / AVATAR AND DOG
A central question regarding the game design is how emotionally invested the players are in the game. Our goal was to create a play experience that had en emotional impact on the player that goes beyond pure entertainment. We believed that this could be achieved by first creating a gloomy narrative set in a - close to - real environment and by creating affordances that makes the player experience the story as being the protagonist rather than observing.  The participants identification with the depicted protagonist of the game and the participants perceived roles in the game indicates that the participants played the game in different ways. We cannot quantify the participants emotional investment but there are trends in the data that indicate how the players felt while playing the game. The data indicates that the players have different perceptions of the protagonist as an avatar. To some he is a rounded character whos fate the players decide, to others he is a projection of player's self in his reality. To avoid a confusion of the character versus the avatar we will refer to the protagonist as the 'protagonist' in the following paragraph.

The second decision the participants had to make in the game was to give the protagonist a name. Six participants(1, 2, 3, 4, 5, 7) chose to give the protagonist a what we define as a serious name. The serious names are names that resemble the participants real name or is a known nickname of theirs while the non-serious names are not. We speculate that the participants chose a serious name because they want to identify with the protagonist rather than distance themselves from him. While picking a non-serious name is a way to create a humorous distance between yourself and the protagonist in the game. This speculation is partly supported by the data. One of the participants(6) who chose a non-serious name was experiencing the whole game as a satire, she clearly had a humorous distance to the entire play experience. Another participant(9) who chose a non-serious name states that he did not identify with the protagonist and that it was a conscious decision to give the protagonist a non-serious name. However data from three of the participants(1, 4, 7) who chose a serious name indicates that they did not identify with the protagonist. Hence the name to protagonist relationship hypothesis does not seem to apply. Instead choosing a serious name may be an expression of how willing you are to invest emotions in the game.

Interestingly the serious name pattern changes when the participants are asked to give their dog a name. Now only two participants(2, 7) chose to give their dog a serious name. This shift might indicate either that the game has made the participants perceive their role in the game differently or that the participants are trying consciously to distance themself from the either the game or the dog in the game. Participant 5 and 9 states that they chose a funny or distancing name to avoid getting too close to the dog. The data of participant 4 indicate the same trend but is less clear cut. Participants 1, 3 and 8's data indicate that they did not yet feel attached to the dog the moment they had to give it a name. Participant 6 was as explained earlier having a satirical distance to the entire game experience.
Interestingly only two participants(6, 8) chose to leash the dog however both of them expressed that they thought it was the correct option, implying that they were afraid of the consequences if they did not leash it. Participant 1, 2, 3, 7 and 9 express that they believe their relationship with the dog would be improved by not leashing it. Participant 4 and 5 both express that leashing it would have made the dog easier to control, but chose to not leash it. The findings indicate that the name can be perceived as an indication of emotional engagement in the game. Moreover it seems that our implementation did a sub par job at creating the necessary emotional bonding to the dog prior to the naming of it.





TO-DO:...
Take the previous written stuff and see if it fits as answers to the three hypotheses. Find more trends in the data. Structure the whole testing paragraph in a better way. At least make subsection titles better. Get more into agency versus avatar versus character and use proper references.
ie. 

Wardrip-Fruin, Noah et al. (2009): "Agency Reconsidered.? Breaking New Ground: Innovation in Games, Play, Practice and Theory. Proceedings of DiGRA 2009, URL: http://www.digra.org/digital-library/publications/agency-reconsidered/

Linderoth, Jonas. (2005): Animated game pieces. Avatars as roles, tools and props. In Aesthetics of Play Conference Proceedings, URL: http://www.aestheticsofplay.org/linderoth.php

Klevjer, Rune (2012): "Enter the Avatar: The Phenomenology of Prosthetic Telepresence in Computer Game?. In The Philosophy of Computer Games (pp. 17-38). Springer Netherlands.

Harrer, S., & Pichlmair, M. (2015). Black Skin White Guns: Becoming Colonizer in Resident Evil 5.




